Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-07-22 ch04-lrmhinf/lrmhinf.tex
Fix broken sentence in robust control intermezzo

Building a good model set $\ModelSet[]$ as in \eqref{eq:lrmhinf:model-set:generic}, hence requires estimating a good value of the overbound $\gamma$ to define the size of the set.
This overbound has important practical implications for the robust controller design.
Specifically, let us denote $\true{\gamma} \isdef \norm{\true\Delta} \isdef \norm{\Delta(\estimated{\Plant}, \true{\Plant})}$.
For an estimation procedure that yields the estimate $\estimated{\gamma}$ of the overbound, a few situations can hence occur.
\begin{itemize}
  \item $\estimated\gamma < \true{\gamma}$: the model set $\ModelSet[]$ is too small and hence $\true{\Plant} \not\in \ModelSet[]$.
  Based on such an estimate, the robust controller may fail to stabilize and perform well for the actual plant $\true{\Plant}$.
  \item $\estimated\gamma \gg \true{\gamma}$: the model set $\ModelSet[]$ is too big such that the robust controller is overly conservative.
  Consequently, the plant is still stabilized by the controller, but the performance of the system may be degraded.
  This  the actual plant is still stabilized by the controller, this can degrade the performance of the control system since it accounts for too many possible plants.
    \item $\estimated\gamma = \true{\gamma}$: the model set is just large enough to contain $\true{\Plant}$ such that both stability and performance are satisfied.
\end{itemize}

>>>>

Building a good model set $\ModelSet[]$ as in \eqref{eq:lrmhinf:model-set:generic}, hence requires estimating a good value of the overbound $\gamma$ to define the size of the set.
This overbound has important practical implications for the robust controller design.
Specifically, let us denote $\true{\gamma} \isdef \norm{\true\Delta} \isdef \norm{\Delta(\estimated{\Plant}, \true{\Plant})}$.
For an estimation procedure that yields the estimate $\estimated{\gamma}$ of the overbound, a few situations can hence occur.
\begin{itemize}
  \item $\estimated\gamma < \true{\gamma}$: the model set $\ModelSet[]$ is too small and hence $\true{\Plant} \not\in \ModelSet[]$.
  Based on such an estimate, the robust controller may fail to stabilize and perform well for the actual plant $\true{\Plant}$.
  \item $\estimated\gamma \gg \true{\gamma}$: the model set $\ModelSet[]$ is too big such that the robust controller is overly conservative.
  Consequently, the actual plant is still stabilized by the controller, but the performance of the system may be degraded as the controller design accounts for too many possible plants.
    \item $\estimated\gamma = \true{\gamma}$: the model set is just large enough to contain $\true{\Plant}$ such that both stability and performance are satisfied.
\end{itemize}
